A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-19 writeup/paper.tex
Finished revising the Related Work section

\section{Background and Related Work}
%\section{Background on Mechanical Turk and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, workforce. MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs).  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.  It has application to other fields like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{novotney-callisonburch:2010:NAACLHLT,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK}.

@@

As the use of MTurk has grown, researchers have become interested in who exactly makes up the Turker population. Early demographic studies by \newcite{ipeirotis:2010:demographics} revealed that Turkers are typically younger and more educated than the population as a whole. The study found that while most Turkers cite money as a motivation for working on MTurk, few cite it as their only motivation. A follow-up study by Ross et al. found that the majority of Turkers were located in the US, 30\% of Turkers were located in India, and that Indian Turkers tend to have lower incomes than US-based Turkers. Ross et al. also suggested that the international presence on MTurk has been growing over time. While there has not yet been a thorough investigation of Turkers' language abilities, \newcite{munro-tily:2011} compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu). No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.

\newcite{irvine:10} Using Mechanical Turk to annotate lexicons for less commonly used languages

 MTurk to build parallel corpora for Machine Translation, a task which requires Turkers to speak two languages with a high level of proficiency.
\cite{ambati_act,ambati_naacl,bloodgood-callisonburch:2010:ACL,zaidan-callisonburch:2011:ACL-HLT2011a,Zbib-etal:2012:NAACL,post-callisonburch-osborne:2012:WMT}

>>>>

\section{Background and Related Work}
%\section{Background on Mechanical Turk and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, workforce. MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs),which hints at its origins.  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge-banerjee-rudnicky:2010:MTURK,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.

\nocite{novotney-callisonburch:2010:NAACLHLT}

@@

A demographic study by \newcite{ipeirotis:2010:demographics} focused on age, gender, martial status, income levels, motivation for working on MTurk, and whether workers used it as a primary or supplemental form of income.  The study contrasted Indian and US workers. 
A number of other studies have informally investigated Turkers' language abilities.  \newcite{munro-tily:2011} compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu).  \newcite{irvine:10} had Turkers evaluate the accuracy of translations that had been automatically inducted from monolingual texts.  They examined translations of 100 words in 42 low-resource languages, reported geolocated countries for their workers (India, the US, Romania, Pakistan, Macedonia, Latvia, Bangladesh and the Philippines).  Irvine and Klementiev discussed the difficulty of quality control and assessing the plausibility of workers' language skills for rare languages, which we address in this paper.

%No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.

Several researchers have investigated using MTurk to build parallel corpora for machine translation, a task which stands to directly benefit from the availability of large volumes of low-cost translations \cite{Germann2001}.  \newcite{ambati_act} conducted a pilot study by posting 25 sentences to MTurk for Spanish, Chinese Hindi, Telugu, Urdu, and Haitian Creole.  In a study of 2000 Urdu sentences, 
\newcite{zaidan-callisonburch:2011:ACL-HLT2011a} presented methods for achieving professional-level translation quality from Turkers by soliciting multiple English translations of each foreign sentence. 
\newcite{Zbib-etal:2012:NAACL} used crowdsourcing to construct a 1.5 million word parallel corpus of dialect Arabic and English, training a statistical machine translation system that produced higher quality translations of dialect Arabic than a system a trained on 100x more Modern Standard Arabic-English parallel data.  \newcite{post-callisonburch-osborne:2012:WMT} used MTurk to build parallel corpora between English and six Indian languages, ranging from .5M to 1.5M words, and use them to demonstrate the efficacy of syntactic approaches to machine translation on verb-final languages.  
Several researchers have examined cost optimization through using active learning techniques to select which sentences or fragments to translate \cite{ambati_naacl,bloodgood-callisonburch:2010:ACL,AmbatiThesis}.
